---
title: "NetCDF subsetting"
author: "Quentin Read"
date: "9/28/2021"
output: html_document
---

First, do a query to get the latitude and longitude values for each cell. We get a matrix for each one in the `stars` object. The first one is latitude and the second longitude.

```{r get latlon}
library(stars)
library(glue)

baseurl <- 'http://thredds.aoos.org/thredds/dodsC/GOA_RUNOFF_DISCHARGE.ncml'

query_latlon <- glue('{baseurl}?lat,lon')

# latlon <- read_ncdf(query_latlon)
```

```{r}
# read using ncdf4
test_latlon <- nc_open(query_latlon)
print(test_latlon)

# get latitude
lat_deg_north <- ncvar_get(test_latlon, "lat")
# get longitude
lon_deg_east <- ncvar_get(test_latlon, "lon")

latlon_df <- data.frame(as.vector(lat_deg_north), as.vector(lon_deg_east))
names(latlon_df) <- c("latitude_deg_north", "longitude_deg_east")
# ggplot(data = latlon_df, aes(x=longitude_deg_east, y=latitude_deg_north)) + geom_tile() + coord_equal()


```

Next, we want to translate Rachael's desired extent into cell indexes so we can do a reduced query for just the cells we need. The first step is to get vectors of lats and longs.

```{r lat lon vectors}
limits <- c(-151.40, 59.44, -151.63, 59.54)
# lat_vec <- as.numeric(latlon[[1]][1,])
# lon_vec <- as.numeric(latlon[[2]][,1])
```

Now find the range of indexes for the desired extent. We have to subtract one because the netCDF is indexed 0-based, and R is 1-based.

```{r index ranges}
# lat_limits <- range(which(lat_vec >= limits[2] & lat_vec <= limits[4])) - 1
# lon_limits <- range(which(lon_vec >= limits[3] & lon_vec <= limits[1])) - 1
# 
# lat_limits
# 
# lon_limits
```

```{r}
# 900 columns and 1810 rows

# get the indexes for latitude values in the desired range
lat_m <- which(lat_deg_north >= limits[2] & lat_deg_north <= limits[4], arr.ind=TRUE)
lat_df <- data.frame(lat_m)
min(lat_df$row); max(lat_df$row)#; unique(lat_df$row)  # 1810 unique rows
min(lat_df$col)-1; max(lat_df$col)-1#; sort(unique(lat_df$col)) 
# So, need all rows, and only certain columns

# get the indexes for longitude values in the desired range
lon_m <- which(lon_deg_east >= limits[3] & lon_deg_east <= limits[1], arr.ind=TRUE)
lon_df <- data.frame(lon_m)
min(lon_df$row)-1; max(lon_df$row)-1#; sort(unique(lon_df$row))
min(lon_df$col); max(lon_df$col)#;unique(lon_df$col)  # 900 unique cols
# So need all cols, and only certain rows

```

For the final query, the dimensions of `q` are ordered `(time, y, x)`. If `y` is latitude and `x` is longitude this should be correct but please check this!

```{r final query}
# query_final <- glue('{baseurl}?q[0:1:12784][{lat_limits[1]}:1:{lat_limits[2]}][{lon_limits[1]}:1:{lon_limits[2]}]')
# 
# query_final <- glue('{baseurl}?q[0:1:12784][{lon_limits[1]}:1:{lon_limits[2]}][{lat_limits[1]}:1:{lat_limits[2]}]')
# 
# dat <- read_ncdf(query_final)
# 
# dim(dat[['q']]) 
```

Dimensions check out!

Let's check the geography:

NOTE: Had to just tweak and then plot, and then tweak and then plot to get the correct indexing.  Never was able to get the correct indexing with the above code. 

```{r map}
# had to arrive at final index numbers by trial and error
# final indexes for y were 353:363, and for x were 314:325 
query_finale <- glue("{baseurl}?lat[353:1:363][314:1:325],lon[353:1:363][314:1:325],q[0:1:12784][353:1:363][314:1:325],time[0:1:12784]")

test_dat <- nc_open(query_finale)

# get latitude
latitude_deg_north <- ncvar_get(test_dat, "lat")
# get longitude
longitude_deg_east <- ncvar_get(test_dat, "lon")

# look at extent of file
plot_df <- data.frame(as.vector(latitude_deg_north), as.vector(longitude_deg_east))
names(plot_df) <- c("latitude_deg_north", "longitude_deg_east")
ggplot(data = plot_df, aes(x=longitude_deg_east, y=latitude_deg_north)) + 
       geom_tile() + coord_equal()

```